Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-10 paper/paper.tex
Improverate the figures

\begin{figure}
    % \includegraphics*{gen-graph-ids.pdf}
    \caption{We get domain filtering. Woohoo.}\label{figure:ids}
\end{figure}

@@

@@

To allow for fast propagation, we create supplemental graphs for paths of length 2, looking at
counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).
We then investigate whether this leads to new constraints being generated. By an assignment, we mean
considering mapping a pattern vertex $p$ to a target vertex $t$ (and not $\bot$) which does not
violate any loop constraints. An assignment pair is two assignments with distinct $p$ and distinct
$t$, which we say is permitted if it does not violate any adjacency constraint. We define the
permitted assignment pair ratio to be the proportion of assignment pairs which are permitted.
Finally, we scatter plot the permitted assignment pair ratio with and without supplemental
graphs\footnote{Because of the large sizes of the domains, we randomly sample one million pairs
rather than considering every pair. In some cases, we have nearly a thousand domains, each with nearly
ten thousand values---a complete quadratic calculation involving even a trivial arithmetic operation
on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal, which
shows that for many instances, we are able to create a substantial number of new constraints at the
top of search; on the other hand, there are also points on the diagonal, which shows that sometimes
this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal. This is
because the use of neighbourhood degree sequence reasoning on supplemental graphs can also lead to
increased domain filtering, which could in turn eliminate a higher proportion of forbidden than
permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal
diminishes, but we are still able to create new constraints for many instances. By the time $k = 3$,
most of the benefit is disappearing---although sometimes we are still able to make a difference, and
bear in mind that sometimes adding just one new constrained pair can vastly reduce the search space.

A closer inspection of the raw data shows that for $k = 3$, nearly all of the instances showing a
strong improvement are from the ``LV'' family of graphs.

\begin{figure*}
    % \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
    % \includegraphics*{gen-graph-constraints-induced.pdf}
    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
\end{figure*}

@@

\begin{figure}
    % \includegraphics*{gen-graph-runtimes.pdf}
    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
\end{figure}

@@

\begin{figure}
    % \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{There are satisfiable instances for small values of $k$. Yay.}\label{figure:which-k}
\end{figure}

@@

\begin{figure}
    % \includegraphics*{gen-graph-versus-cp.pdf}
    \caption{A righteous spanking.}\label{figure:versus-cp}
\end{figure}

>>>>

\begin{figure}
    \includegraphics*{gen-graph-ids.pdf}
    \caption{The amount of domain reduction achieved for the induced problem, with increasing values
    of $k$. The $y$ value shows for how many instances we may reduce the domain size to be at most
    the $x$ proportion of the size the domains would be for the maximum common subgraph
    problem.}\label{figure:ids}
\end{figure}

@@

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-constraints-induced-0.pdf}
    \includegraphics*{gen-graph-constraints-induced-1.pdf}
    \includegraphics*{gen-graph-constraints-induced-2.pdf}
    \includegraphics*{gen-graph-constraints-induced-3.pdf}
    \includegraphics*{gen-graph-constraints-induced-4.pdf}
    \includegraphics*{gen-graph-constraints-induced-5.pdf}

    \caption{For the induced problem, the proportion of pairs of assignments from the filtered
    domains which are not permitted simultaneously, without path constraints on the $x$-axis and
    with path constraints on the $y$-axis, for increasing values of $k$.}\label{figure:constraints}
\end{figure*}

@@

To allow for fast propagation, we create supplemental graphs for paths of length 2, looking at
counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).
We then investigate whether this leads to new constraints being generated. By an assignment, we mean
considering mapping a pattern vertex $p$ to a target vertex $t$ (and not $\bot$) which does not
violate any loop constraints. An assignment pair is two assignments with distinct $p$ and distinct
$t$, which we say is permitted if it does not violate any adjacency constraint. We define the
permitted assignment pair ratio to be the proportion of assignment pairs which are permitted.
Finally, we scatter plot the permitted assignment pair ratio with and without supplemental
graphs\footnote{Because of the large sizes of the domains, we randomly sample one million pairs
rather than considering every pair. In some cases, we have nearly a thousand domains, each with
nearly ten thousand values---a complete quadratic calculation involving even a trivial arithmetic
operation on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal,
which shows that for many instances, we are able to create a substantial number of new constraints
at the top of search; on the other hand, there are also points on the diagonal, which shows that
sometimes this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal.
This is because the use of neighbourhood degree sequence reasoning on supplemental graphs can also
lead to increased domain filtering, which could in turn eliminate a higher proportion of forbidden
than permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the
diagonal diminishes, but we are still able to create new constraints for many instances. By the time
$k = 3$, most of the benefit is disappearing---although sometimes we are still able to make a
difference, and bear in mind that sometimes adding just one new constrained pair can vastly reduce
the search space.  A closer inspection of the raw data shows that for $k \ge 3$, nearly all of the
instances showing a strong improvement are from the ``LV'' family of graphs.

@@

\begin{figure}
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{The cumulative number of instances solved over time, for the induced and non-induced
    problems, with different values of $k$. We also show the results of iteratively decreasing $k$
    until a solution is found, and in the induced case, the performance of a leading maximum common
    subgraph algorithm.}\label{figure:runtimes}
\end{figure}

@@

\begin{figure}
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The larger instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@
